---
title: "01_development"
author: "Darren Norris"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_depth: 3
    fig_caption: yes
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 3
    number_sections: yes
    extra_dependencies: flafter
    highlight: tango
    includes:
      in_header: preamble.txe
always_allow_html: yes
urlcolor: blue
toc-title: Contents
header-includes:
  - \counterwithin{figure}{section}
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  echo = TRUE, collapse = TRUE,
  comment = "#>" 
  )
def_hook <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  out <- def_hook(x, options)
  return(paste("\\begin{framed}\\begin{verbatim}", x, "\\end{verbatim}\\end{framed}", collapse = "\n"))
})
```

\newpage{}

# Load and prep data
## Packages
# Pacotes necessarios:
```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(gridExtra)
```

## Journal impact

[Scopus CiteScore](https://www.elsevier.com/solutions/scopus/how-scopus-works/metrics/citescore) and [JCR Journal Impact Factor ("JIF")](https://clarivate.com/webofsciencegroup/solutions/journal-citation-reports/), downloaded on 4 and 23 January 2023 respectively. 
Using 11 years (2011 to 2021), as 2011 is first year for CiteScore and also follows the definition of conservation threats and actions published in 2008 (Salafsky et. al., 2008 A Standard Lexicon for Biodiversity Conservation: Unified Classifications of Threats and Actions https://doi.org/10.1111/j.1523-1739.2008.00937.x). 
The companies classify journals differently and the folder [data](https://github.com/darrennorris/hey-jude/tree/main/data) has impact of journals in Nature and Landscape Conservation (CiteScore: https://github.com/darrennorris/hey-jude/tree/main/data/scopus_citescore) and Biodiversity Conservation (JIF https://github.com/darrennorris/hey-jude/tree/main/data/clarivate_JCR).

Code below loads and joins CiteScore and JIF.
```{r load-journal-impact}
jcr_11a21 <-read_excel("data/clarivate_JCR/JCR2011a2021.xlsx", 
           na = c("", "NA", "N/A"))
```

