---
  title: "02_wos_scopus"
author: "Darren Norris"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
  toc: yes
toc_float: yes
toc_depth: 3
fig_caption: yes
bookdown::pdf_document2:
  toc: yes
toc_depth: 3
number_sections: yes
extra_dependencies: flafter
highlight: tango
includes:
  in_header: preamble.txe
always_allow_html: yes
urlcolor: blue
toc-title: Contents
header-includes:
  - \counterwithin{figure}{section}
---
  
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  echo = TRUE, collapse = TRUE,
  comment = "#>" 
)
def_hook <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  out <- def_hook(x, options)
  return(paste("\\begin{framed}\\begin{verbatim}", x, "\\end{verbatim}\\end{framed}", collapse = "\n"))
})
```

\newpage{}

## Seaarch strategy
1. Make sure WOS and Scopus results are same for same journal.
2. Results for same journal include all those from Conservation Evidence and Williams 2020 
The past and future role of conservation science in saving
biodiversity https://doi.org/10.1111/conl.12720

## Packages
```{r load-packages, warning=FALSE, message=FALSE}
# Data processing and presentation
library(plyr) # plyr before tidyverse
library(tidyverse)
library(stringr)
library(textclean)
library(readxl)
library(gridExtra)
library(magrittr)
# bibliometric
library(rscopus)
library(bibliometrix)
library(metagear)


```

Names of journals
```{r journal-names}
cs_NLC_11a21 <-read_excel("data/scopus_citescore/citescore_NLC_2011a2021.xlsx", 
           na = c("", "NA", "N/A")) 
jn_nlc <- unique(cs_NLC_11a21$SourceTitle)
jn_multi <- c("Nature", "Science", "Scientific Reports", "PeerJ", "PLoS ONE")


```



Test scopus search 
```{r get-pii}
options("elsevier_api_key" = "0c6d56570f89faf767669d9ae8cdd873")
have_api_key()
print(rscopus::get_api_key(), reveal = TRUE)

# Abstracts and doi from pii
 x = abstract_retrieval("S1053811915002700", identifier = "pii",
   verbose = FALSE)
 # Abstract text
 x$content$`abstracts-retrieval-response`$coredata$`dc:description`
 # Doi
 x$content$`abstracts-retrieval-response`$coredata$`prism:doi`
 
# scopus_search fails. Bad Request (HTTP 400).
 dsge_query <- rscopus::scopus_search("TITLE-ABS-KEY(DSGE) OR TITLE-ABS-KEY(\"Dynamic Stochastic General Equilibrium\")", view = "COMPLETE")
 


```


Scopus search 8/3/2023 Bio Con with 287 articles.
Will include several that are not focused on vertebrates as keywords are not author keywords so include incorrect terms. Will need to screen Abstracts.
( SRCTITLE ( "Biological Conservation" ) AND TITLE-ABS-KEY ( "vertebrate" OR "vertebrates" OR fauna ) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE , "ar" ) )

```{r build-search}

cn <-read_excel("data/common_names.xlsx") %>% 
  mutate(common_name = str_to_lower(str_trim(as.character(common_name)))) %>% 
  distinct()
         
cstring <- paste(cn$common_name, collapse=" OR ")

```


Using only title and keywords = 92 with study of plants as has vertebrate in keywords.
( SRCTITLE ( "Biological Conservation" ) AND ( TITLE ( "vertebrate" OR "vertebrates" OR fauna ) ) OR KEY ( "vertebrate" OR "vertebrates" OR fauna ) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE , "ar" ) )

Broaden gets 2024
( SRCTITLE ( "Biological Conservation" ) AND TITLE-ABS-KEY ( wildlife* OR "vertebrate" OR "vertebrates" OR fauna* OR bushmeat OR herbivore* OR felid* OR canid* OR bird OR reptile OR snake OR anteaters OR armadillo OR sloth OR lizard OR fish OR amphibian OR ape OR monkey OR gibbon OR crocodile OR turtle OR frog OR toad or tortoise OR bat OR shark OR whale OR ray OR eel OR ) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE,"ar" ) )

expand search with mammal common names = 2329
( SRCTITLE ( "Biological Conservation" ) AND TITLE-ABS-KEY ( wildlife* OR { vertebrate } OR { vertebrates } OR fauna* OR bushmeat OR herbivore* OR felid* OR canid* OR bird OR reptile OR snake OR anteaters OR armadillo OR sloth OR lizard OR fish OR amphibian OR ape OR monkey OR gibbon OR crocodile OR turtle OR frog OR toad or tortoise OR bat OR shark OR whale OR ray OR eel OR Platypus OR Echidna OR Marsupial OR Opossum OR "Monito del Monte" OR Dasyuromorph OR antechinuse OR "Tasmanian devil" OR dunnart OR quoll OR Numbat OR Bilbies OR Bandicoot OR mole OR Diprotodont OR Koala OR Wombats OR possum OR cuscuses OR glider OR bettong OR kangaroo OR potoroos OR wallabie OR shrew OR mole OR aardvark OR Hyrax OR Elephant OR Dugong OR Manatee OR sloth OR anteater OR tamandua OR armadillo OR Treeshrew OR lemur OR Primate OR Aye-aye OR loris OR Galago OR Tarsier OR monkey OR tamarin OR marmoset OR titi OR saki OR uakari OR Gibbon OR "Great ape" OR rabbit OR hare OR pika OR rodent OR squirrel OR Springhare OR Beaver OR Gopher OR Porcupine OR rat OR mouse OR Gundi OR viscacha OR capybara OR Hutia OR chinchillas OR Tuco-tuco OR Agouti OR Paca OR Pacarana OR pig OR coypu OR nutria OR rock-rat OR degu OR jerboa OR hamster OR vole OR gerbil OR dormice OR dormouse OR zokor OR beaver OR chipmunk OR "prairie dog" OR marmot OR Hedgehog OR solenodon OR ungulate OR cetacean OR bat OR pangolin OR carnivor OR camel OR llama OR Peccaries OR peccary OR hippo OR ruminant OR whale OR dolphin OR Beluga OR Narwhal OR Porpoise OR Chevrotain OR Pecoran OR Pronghorn OR okapi OR giraffe OR Deer OR goat OR antelope OR Bat OR Megabat OR Microbat OR "flying fox" OR Tapir OR rhino OR Feran OR Pangolin OR civet OR linsang OR cat OR hyena OR aardwolf OR mongoose OR felid OR dog OR bear OR panda OR badger OR skunk OR weasel OR marten OR otter OR badger OR wolverine OR mink OR ferret OR raccoon OR coati OR Pinniped OR Walrus OR "sea lion" OR sea) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE,"ar" ) )

```{r check-scopus}
# load bio con results
bcfile <- "data/scopus_20230308/scopus_biocon02.bib"
bcrefs <- bibliometrix::convert2df(file = bcfile, dbsource = "scopus", 
                                     format = "bibtex") 
# load CE refs
cedat <-read_excel("data/studydat_fordarrenn_24_02_2023DN.xlsx", 
           na = c("", "NA", "N/A"), sheet="study_dois_start2011")
cedat %>% filter(journal.name=="Biological Conservation") %>% 
  pull(doi_clean) -> dois_biocon # 69

bcrefs %>% filter(DI %in% dois_biocon) # 53

cedat %>% left_join(bcrefs, by=c("doi_clean"="DI")) %>% 
  filter(journal.name =="Biological Conservation") %>% 
  write.csv2("data/bcjoin.csv", row.names = FALSE)
```



Searching multidisciplinary returns 10549. Need to use ISSN to pull journals.
( SRCTITLE ( {Nature} OR {Science} OR {Scientific Reports} OR {PeerJ} OR {PLoS ONE} ) AND TITLE-ABS-KEY ( "vertebrate" OR "vertebrates" OR fauna ) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE , "ar" ) )

With ISSN returns 5179 articles.
( ISSN ( "0028-0836" OR "0036-8075" OR "2045-2322" OR "2167-8359" OR "1932-6203" ) AND TITLE-ABS-KEY ( "vertebrate" OR "vertebrates" OR fauna ) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE , "ar" ) )

With conservation or biodiversity returns 1130 articles.
( ISSN("0028-0836" OR "0036-8075" OR "2045-2322" OR "2167-8359" OR "1932-6203") AND TITLE-ABS-KEY ( " vertebrate " OR " vertebrates " OR " fauna " ) AND TITLE-ABS-KEY ( " conservation" OR " biodiversity" ) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE,"ar" ) )

With mammal common names = 6919
( ISSN("0028-0836" OR "0036-8075" OR "2045-2322" OR "2167-8359" OR "1932-6203") AND TITLE-ABS-KEY ( wildlife* OR { vertebrate } OR { vertebrates } OR fauna* OR bushmeat OR herbivore* OR felid* OR canid* OR bird OR reptile OR snake OR anteaters OR armadillo OR sloth OR lizard OR fish OR amphibian OR ape OR monkey OR gibbon OR crocodile OR turtle OR frog OR toad or tortoise OR bat OR shark OR whale OR ray OR eel OR Platypus OR Echidna OR Marsupial OR Opossum OR "Monito del Monte" OR Dasyuromorph OR antechinuse OR "Tasmanian devil" OR dunnart OR quoll OR Numbat OR Bilbies OR Bandicoot OR mole OR Diprotodont OR Koala OR Wombats OR possum OR cuscuses OR glider OR bettong OR kangaroo OR potoroos OR wallabie OR shrew OR mole OR aardvark OR Hyrax OR Elephant OR Dugong OR Manatee OR sloth OR anteater OR tamandua OR armadillo OR Treeshrew OR lemur OR Primate OR Aye-aye OR loris OR Galago OR Tarsier OR monkey OR tamarin OR marmoset OR titi OR saki OR uakari OR Gibbon OR "Great ape" OR rabbit OR hare OR pika OR rodent OR squirrel OR Springhare OR Beaver OR Gopher OR Porcupine OR rat OR mouse OR Gundi OR viscacha OR capybara OR Hutia OR chinchillas OR Tuco-tuco OR Agouti OR Paca OR Pacarana OR pig OR coypu OR nutria OR rock-rat OR degu OR jerboa OR hamster OR vole OR gerbil OR dormice OR dormouse OR zokor OR beaver OR chipmunk OR "prairie dog" OR marmot OR Hedgehog OR solenodon OR ungulate OR cetacean OR bat OR pangolin OR carnivor OR camel OR llama OR Peccaries OR peccary OR hippo OR ruminant OR whale OR dolphin OR Beluga OR Narwhal OR Porpoise OR Chevrotain OR Pecoran OR Pronghorn OR okapi OR giraffe OR Deer OR goat OR antelope OR Bat OR Megabat OR Microbat OR "flying fox" OR Tapir OR rhino OR Feran OR Pangolin OR civet OR linsang OR cat OR hyena OR aardwolf OR mongoose OR felid OR dog OR bear OR panda OR badger OR skunk OR weasel OR marten OR otter OR badger OR wolverine OR mink OR ferret OR raccoon OR coati OR Pinniped OR Walrus OR "sea lion" OR seal ) AND TITLE-ABS-KEY ( " conservation" OR " biodiversity" ) ) AND PUBYEAR > 2010 AND PUBYEAR < 2022 AND ( LIMIT-TO ( DOCTYPE,"ar" ) )

Search for abstracts with stronger sentiment.

( TITLE-ABS-KEY( wildlife* OR fauna* OR bushmeat OR herbivore* OR felid* OR canid* OR bird OR reptile OR snake OR anteaters OR armadillo OR sloth OR lizard OR fish OR amphibian OR ape OR monkey OR gibbon OR crocodile OR turtle OR frog OR toad or tortoise OR bat OR shark OR whale OR ray OR eel OR Platypus OR Echidna OR Marsupial OR Opossum OR "Monito del Monte" OR Dasyuromorph OR antechinuse OR "Tasmanian devil" OR dunnart OR quoll OR Numbat OR Bilbies OR Bandicoot OR mole OR Diprotodont OR Koala OR Wombats OR possum OR cuscuses OR glider OR bettong OR kangaroo OR potoroos OR wallabie OR shrew OR mole OR aardvark OR Hyrax OR Elephant OR Dugong OR Manatee OR sloth OR anteater OR tamandua OR armadillo OR Treeshrew OR lemur OR Primate OR Aye-aye OR loris OR Galago OR Tarsier OR monkey OR tamarin OR marmoset OR titi OR saki OR uakari OR Gibbon OR "Great ape" OR rabbit OR hare OR pika OR rodent OR squirrel OR Springhare OR Beaver OR Gopher OR Porcupine OR rat OR mouse OR Gundi OR viscacha OR capybara OR Hutia OR chinchillas OR Tuco-tuco OR Agouti OR Paca OR Pacarana OR pig OR coypu OR nutria OR rock-rat OR degu OR jerboa OR hamster OR vole OR gerbil OR dormice OR dormouse OR zokor OR beaver OR chipmunk OR "prairie dog" OR marmot OR Hedgehog OR solenodon OR ungulate OR cetacean OR bat OR pangolin OR carnivor OR camel OR llama OR Peccaries OR peccary OR hippo OR ruminant OR whale OR dolphin OR Beluga OR Narwhal OR Porpoise OR Chevrotain OR Pecoran OR Pronghorn OR okapi OR giraffe OR Deer OR goat OR antelope OR Bat OR Megabat OR Microbat OR "flying fox" OR Tapir OR rhino OR Feran OR Pangolin OR civet OR linsang OR cat OR hyena OR aardwolf OR mongoose OR felid OR dog OR bear OR panda OR badger OR skunk OR weasel OR marten OR otter OR badger OR wolverine OR mink OR ferret OR raccoon OR coati OR Pinniped OR Walrus OR "sea lion" OR seal ) AND TITLE-ABS-KEY ( " conservation success" OR "conservation solution" OR "biodiversity crisis" OR  "extinction crisis" OR "biodiversity loss") ) AND PUBYEAR > 2019 AND PUBYEAR < 2023 AND ( LIMIT-TO ( DOCTYPE,"ar" ) )

Load results 835 Abstracts with potentially stronger sentiments.
```{r load-stronger}

```

